7_cluster_figs

### 2018-03-28 7_cluster_figs.Rmd

# knitr::read_chunk('R/utils.R')

source('R/utils.R')

@@

s <- s_clust_map(m, tracts, data, blocked_tracts, size_coef = .75)
s

@@

```{r}
f <- h_clust_map(m, tracts, data, b, j, size_coef = .75)
f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

@@

```{r}
set.seed(1250)
k     <- 36
g     <- spectral_cluster(g, sigma = sigma, k = k, nreps = 1000)
```

@@

s <- s_clust_map(m, tracts, data, blocked_tracts, size_coef = .75)
s

@@

```{r}
f <- h_clust_map(m, tracts, data, b, j, size_coef = .75)
f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

@@

<!-- # Atlanta -->

<!-- ```{r} -->
<!-- city    <- 'Atlanta' -->
<!-- in_data <- read_data(city, all_data) -->
<!-- data    <- in_data$data -->
<!-- tracts  <- in_data$tracts -->

<!-- b <- h_clust(tracts, data) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- g <- construct_information_graph(tracts = tracts,  -->
<!-- 								 data = data,  -->
<!-- 								 divergence = js_dist) -->

<!-- sigma <- 30 -->
<!-- plot_spectrum(g, sigma) -->
<!-- ggsave(paste0('figs/spectrum_', city, '.pdf')) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- k     <- 26 -->
<!-- g     <- spectral_cluster(g, sigma = sigma, k = k, nreps = 1000) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- input <- group_data(tracts, data, g)  -->
<!-- blocked_tracts <- input$blocked_tracts -->
<!-- blocked_data <- input$blocked_data -->

<!-- blocked_tracts %>%  -->
<!--     ggplot() +  -->
<!--     geom_sf(aes(fill = as.character(cluster))) + -->
<!--     guides(fill = FALSE) -->
<!-- ``` -->

<!-- ## Hierarchical Clustering -->

<!-- ```{r} -->
<!-- a <- h_clust(blocked_tracts, blocked_data) -->
<!-- compare_hclusts(a, b) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- j <- 3 -->
<!-- m <- prominence_map(tracts, data) +  -->
<!--         guides(fill = FALSE)  -->

<!-- s <- s_clust_map(m, tracts, data, blocked_tracts, size_coef = 1) -->
<!-- s -->

<!-- ggsave(paste0('figs/sclust_', city, '.pdf'), width = map_width, height = map_height) -->

<!-- h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = 1) -->
<!-- h -->
<!-- ggsave(paste0('figs/mixed_', city,'.pdf'), width = map_width, height = map_height) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- f <- h_clust_map(m, tracts, data, b, j, size_coef = 1) -->
<!-- f -->
<!-- ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- df <- df %>%  -->
<!--     rbind(data_frame( -->
<!--         city = city,  -->
<!--         k = k,  -->
<!--         j = j, -->
<!--         hclust = cumsum(rev(b$height))[j], -->
<!--         mixed = cumsum(rev(a$height))[j] -->
<!--     )) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- loss_curves <- loss_curves %>% -->
<!--     rbind(data_frame( -->
<!--         city = city,  -->
<!--         k = 1:length(a$height), -->
<!--         h_val = rev(b$height)[1:length(a$height)], -->
<!--         m_val = rev(a$height) -->
<!--     )) -->

<!-- MI <- MI %>%  -->
<!--     rbind(data_frame( -->
<!--         city = city,  -->
<!--         I_XY = data %>%  -->
<!--             spread(key = group, value = n) %>%  -->
<!--             select(-tract) %>%  -->
<!--             mutual_info() -->
<!--     )) -->
<!-- ``` -->

@@

set.seed(1234)
```

@@

h <- h_clust_map(m, blocked_tracts, blocked_data, a, j, size_coef = .75)
h
ggsave(paste0('figs/mixed_', city,'.pdf'), width = map_width, height = map_height)
```

```{r}
f <- h_clust_map(m, tracts, data, b, j, size_coef = .75)
f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

>>>>

source('R/utils.R')
```

@@

s <- s_clust_map(m, tracts, data, blocked_tracts, size_coef = .75)

s

@@

f <- h_clust_map(m, tracts, data, b, j, size_coef = .75)
f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

@@

set.seed(1250)

k     <- 36
g     <- spectral_cluster(g, sigma = sigma, k = k, nreps = 1000)
```

@@

s <- s_clust_map(m, tracts, data, blocked_tracts, size_coef = .75)

@@

f <- h_clust_map(m, tracts, data, b, j, size_coef = .75)

f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```

@@

@@

set.seed(1234)

@@

h
ggsave(paste0('figs/mixed_', city,'.pdf'), width = map_width, height = map_height)
```

f <- h_clust_map(m, tracts, data, b, j, size_coef = .75)

f
ggsave(paste0('figs/hclust_', city,'.pdf'), width = map_width, height = map_height)
```
